---
title: "case_study"
author: "Weijia Xiong"
date: "10/8/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(leaflet)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## do data science!!

```{r}
library(p8105.datasets)
data("nyc_airbnb")
```


* how are air bnb prices related to rent in the neighborhood?
* which neighborhood is most expensive and which is cheapest?
* do hosts with multiple sites have higher prices or ratings?
* does price have any relation to ratings?
* is average length of stay related to neighborhood? price? etc?

## let's answer some questions...

```{r}
nyc_airbnb =
  nyc_airbnb %>% 
  mutate(
    stars = review_scores_location / 2,
    borough = neighbourhood_group
  )
```


```{r}
nyc_airbnb %>%
  mutate(neighbourhood = as.factor(neighbourhood)) %>%
  filter(borough == "Manhattan") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price, na.rm = TRUE)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip() + 
  ylim(0, 1000)
```


```{r}
price_neighborhood = 
  select(nyc_airbnb,neighbourhood, price) %>%
  group_by(neighbourhood) %>%
  summarise(
    mean_price = mean(price)
  ) %>%
  arrange(
   -mean_price
  )
```


```{r}
nyc_airbnb %>% 
  group_by(borough, room_type) %>% 
  summarize(med_price = median(price, na.rm = TRUE)) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = med_price
  )
```

```{r}
nyc_airbnb %>% 
  filter(borough == "Staten Island", room_type == "Shared room")
```

```{r}
nyc_airbnb %>% 
  count(borough, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```


```{r}
nyc_airbnb %>%
 group_by(neighbourhood_group, neighbourhood) %>%
 summarize(
   mean_price = mean(price, na.rm = TRUE),
   mean_review = mean(review_scores_location, na.rm = TRUE)
 ) %>% 
  ggplot(aes(x = mean_review, y = mean_price)) + 
  geom_point() + 
  facet_grid(~neighbourhood_group)
```

```{r}
nyc_airbnb %>% 
  count(neighbourhood)
```

```{r}
nyc_airbnb %>% 
  filter(neighbourhood == "Astoria") %>% 
  ggplot(aes(x = stars, y = price)) + 
  geom_point()
```


## spatial locations

```{r}
nyc_airbnb %>%
  filter(
    borough == "Manhattan",
    price < 1000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = .3) + 
  facet_grid(~room_type)
```


This map requires knitting to html.

```{r}
pal <- colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$stars)
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  mutate(
    label = str_c("<b>Stars: ", stars, "</b><br>Price: ", price , sep = "")
  ) %>% 
  sample_n(5000) %>% 
  leaflet() %>% 
  addTiles() %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(
    ~lat, ~long,
    color = ~pal(stars),
    radius = 1,
    popup = ~ label)
```